---
title: "Code Book"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('runAnalysis.R')
```

## Getting And Cleaning Data - Final Project

This is a code book describing the various files in this project, and documenting the format of averages.txt

## Files

  - runAnalysis.R - contains the logic for generating the tidy data from the data set.
  - general.R - some utility functions for using popd/pushd to enter/leave directories in a shell-like manner
  - averages.txt - file generated by runAnalysis which contains the tidy data result. See the section below for details.
  - README.rmd - this file, used to generate the README.md and run the runAnalysis.R script.

## Code Book

The output file (averages.txt) represents a summary of all subject/activity pairs, and their averages for various measurements which were taken. There are Gyroscope and Accelerometer readings with various levels of integration/derivation, e.g. for calculating Jerk, Acceleration, mean, standard deviation. Each of these readings has been averaged and put into the output file.

For example, Subject 3 has his WALKING activity summarized for the average of all his walking data.

The data is in a file called averages.txt with the following columns:

```{r codebook, echo=FALSE, results='markup'}
  idx <- 1
  for (name in names(merged_data)){ cat(paste(idx,name,'\r\n')); idx <- idx+1}
```

In the above table, all values *except* Activity and Subject are the aggregate mean of their values in the merged test/training sets.
